### 2017-01-12 doc/manuscript.Rmd
First (rough) draft of discussion - limitations

Limitations:
- While GEE is well suited to longitudinal datasets.. threre is a possibility
given teh complex biology that the temporal associations can not be adequately
analyzed using current methodologies. IN particular, an important issue si taht
we did not quantify TAGFA at each of the three visits and so can not directed
infer changes in TAGFA with changes in IR. However, given potential feedback
between IR and TAGFA, this may in fact be a strength for this particular
association given we are trying to predict how a FA at one time point can
predict future values.
- While PLS is a well-established technique for constructing predictive models
of high dimensionality data strcutures, it can not adjust for potential
confounders and other effect modifiers. Likewise, PLS is not able to handle
longitudinal data so only the baseline visit was used in the PLS analysis.
However, given the limitation, there results are concordant between GEE and PLS
models.
- Our population was predocminiately female and of euro ancestry, who were at 
riskj for diabetes at study enrollment, and as such our results may not be
generalizable to other populations.
- Given the complex biology underlying the variables of interest, there many
some residual confounding we are unaware of or have not been able to adjust for.
However, we have taken extensive precautions for trying to ID confounders
through the DAG models and QIC computations.
- TAGFA may fluctuate daily, but we had participants come in fasted in the morning

>>>>

## Limitations

There are a few important limitations to our study. In addition to the
observational nature of the cohort, the biology underlying the interaction
between TAGFA, insulin secretion, and insulin sensitivity is complex and
multifacetted {{?}} and as such there may be some residual confounding we were
unaware of or had not been able to adjust for. However, we have taken extensive,
empirically based precautions in identifying potential confounders and mediators
through the use of the DAG modeling, relying on previous literature, and through
QIC modeling fitting methods.

TAGFA can fluctuate substantially throughout the day and to control for this all
PROMISE participants came for their clinic visits in the morning in a fasted
state. Some of the inherent variability in TAGFA fluctuation can be managed by
standardizing the data collection time, though there may still be some
{{residual error? random error?}}.

Since TAGFA were only quantified at the baseline visit and as such we cannot
investigate whether there are concomitant changes in TAGFA and the metabolic
measures over time. In relation to this limitation, while GEE is well suited to
longitudinal datasets, the complex biology and temporal nature of the
associations may restrict the ability of GEE to appropriately analyze and
interpret the data. However, to maximize the potential of GEE, we used the model
to infer that a given value of TAGFA could predict values of insulin sensitivity
or beta-cell function over a 6 year period. This in our view is a strength of
our analysis, as it reduces the chance of reverse causality given the tight
integration of the glucose and fatty acid metabolism pathways, as well as uses
GEE modeling appropriately {{? another word}}.

PLS is a well-established technique for constructing predictive models
of high dimensionality data structures (i.e. fatty acid composition), however a
limitation is that the initial models analyzed through PLS and the final
computed scores are not able to control for potential confounders and other
effect modifiers. Likewise, PLS is not able to handle longitudinal data so only
the baseline visit was used in the PLS analysis. In light of these limitations,
we still observe concordant results between the PLS and GEE analyses {{ add more }}.

Even with these limitations, our study also has several major strengths,
including the longitudinal design and the rigorous statistical techniques and
methods applied in analyzing the data. These statistical techniques are
specifically suited to investigating temporal relationships and to handling the
multivariate nature of the data. Lastly, our cohort contains highly detailed and
comprehensive variable measurements at each collection visit, as well as having
both concentration and mol% data for the fatty acids.
